### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - annealing xrd - added draft paragraphs

>>>>

The crystallization events of the bulk and film were confirmed with annealing \acrshort{xrd}. The bulk and films were subjected to no treatment, 120, 140, 145, 170, 200, 250, 290, and 320\degree C heat treatments because \acrshort{xrd}. This was to confirm the location of the \Tg~ and \Tx s, as well as to identify which metallic compounds these phases were.

These results showed the crystallization process of the glass is;

Glass $\rightarrow$ Mg$_{51}$Zn$_{20}$ $\rightarrow$ Mg $\rightarrow$ Ca$_{2}$Mg$_{5}$Zn$_{5}$ $\rightarrow$ MgZn $\rightarrow$ Ca$_{2}$Mg$_{5}$Zn$_{13}$

These phase appear to metastable.
